POMDP comparisons across sigma_m, sigma_g

### 2017-12-29 appendix/appendix.Rmd
longer runs at 0.95 for smoother results

```{r eval=TRUE}
dir.create(log_dir)
options(mc.cores=9)

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 0.00000002,
             timeout = 15000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

@@

static_sims <- 
 map_dfr(models, function(m){
            do_sim <- function(policy) sim_pomdp(
                        m$transition, m$observation, m$reward, discount, 
                        x0 = x0, Tmax = Tmax, policy = policy, reps = reps)$df
            map_dfr(policies, do_sim, .id = "method")
          }, .id = "scenario")

@@

```{r pomdp_sims}
# slower!
unif_prior <- rep(1, length(states)) / length(states)
pomdp_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
             sim_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                       unif_prior, x0 = x0, Tmax = Tmax, alpha = .y,
                       reps = reps)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario")
```

@@

```{r}
i <- meta %>% filter(sigma_g == 0.1, sigma_m ==0) %>% pull(scenario) %>% as.integer()
m <- models[[i]]
mdp <- MDPtoolbox::mdp_policy_iteration(m$transition, m$reward, discount) 
```

```{r}
bind_rows(policy_table,
  data.frame(state = states, 
             policy = "sdp 0.1",
             harvest = actions[mdp$policy],
             stringsAsFactors = FALSE)) %>% 
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line()  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8))
```

>>>>

```{r}
options(mc.cores=1)
```

```{r eval=FALSE}
dir.create(log_dir)

@@

      sarsop(models[[i]]$transition,
             models[[i]]$observation,
             models[[i]]$reward,
             discount = discount,
             precision = 0.00000002,
             timeout = 25000,
             log_dir = log_dir,
             log_data = log_data)
    })
)

@@

set.seed(12345)
static_sims <- 
 map_dfr(models, function(m){
            do_sim <- function(policy) sim_pomdp(
                        m$transition, m$observation, m$reward, discount, 
                        x0 = x0, Tmax = Tmax, policy = policy, reps = reps)$df
            map_dfr(policies, do_sim, .id = "method")
          }, .id = "scenario")

@@

```{r pomdp_sims}
# slower!
unif_prior <- rep(1, length(states)) / length(states)
set.seed(12345)

pomdp_sims <- 
  map2_dfr(models[as.integer(meta$scenario)], alphas, function(.x, .y){
             sim_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                       unif_prior, x0 = x0, Tmax = Tmax, alpha = .y,
                       reps = reps)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario")
```

@@

```{r}
i <- meta %>% filter(sigma_g == 0.15, sigma_m ==0) %>% pull(scenario) %>% as.integer()
m <- models[[i]]
mdp <- MDPtoolbox::mdp_policy_iteration(m$transition, m$reward, discount) 
```

```{r}
bind_rows(policy_table,
  data.frame(state = states, 
             policy = "sdp 0.15",
             harvest = actions[mdp$policy],
             stringsAsFactors = FALSE)) %>% 
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line()  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8))
```
